\TITLE

### 2020-12-31 vonLaszewski-covid.tex
Updates from Overleaf

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_CasesNEW.pdf}
        \caption{Cummulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_DeathNEW.pdf}
        \caption{Cumulatice error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}

>>>>

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.90\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_CasesNEW2.pdf}
        \caption{Cummulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}
    \begin{subfigure}{.90\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_DeathNEW2.pdf}
        \caption{Cumulatice error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
